---
title: "Module 2, Assignment 3"
author: "Ellen Bledsoe"
date: "2023-02-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

1.  Load both the `palmerpenguins` package and the `tidyverse` package into the work space. (2 points)

    ```{r message = FALSE}
    # Load library
    library(palmerpenguins)
    library(tidyverse)
    ```

    ------------------------------------------------------------------------

#### OPTIONAL

```{r}
# Add to Environment
penguins <- penguins
```

------------------------------------------------------------------------

1.  There are 8 columns in the `penguins` data frame. Determine if each variable is continuous or categorical and record your answer below.

    Note: the `year` column can be considered continuous or categorical. *For this assignment, we will consider it continuous.*

    ***Answers:***

    -   ***species: categorical***

    -   ***island: categorical***

    -   ***bill_length_mm: continuous***

    -   ***bill_depth_mm: continuous***

    -   ***flipper_length: continuous***

    -   ***body_mass_g: continuous***

    -   ***sex: categorical***

    -   ***year: continuous***

2.  Produce a histogram plot (just one, not multiple on the same plot). Write 1-2 sentences describing what information you can gather from plot.

```{r warning=FALSE}
# Histogram
ggplot(penguins, aes(bill_depth_mm)) +
  geom_histogram(bins = 20) +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label") +
  theme_bw()
```

***Description: Depends on their plot***

4.  Create a multiple density plot. Make sure we can see each density plot (make sure one isn't blocking another) (3 points). Write 1-2 sentences describing what information you can gather from plot.

```{r}
# Multiple density plot
ggplot(penguins, aes(body_mass_g, color = island, fill = island)) +
  geom_density(alpha = 0.5) +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label",
       color = "Legend Label",
       fill = "Capitalized Label") +
  scale_fill_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  scale_color_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  theme_bw()
```

***Description: Depends on their plot***

5.  Create a box-and-whisker plot. Changing the color of the boxes is optional (if you want to get super fancy, you can change the color based on a different variable). Make sure to add points to the plot. Write 1-2 sentences describing what information you can gather from plot.

```{r warning=FALSE}
# Box and whisker plot
ggplot(penguins, aes(species, flipper_length_mm, color = species)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.5, width = 0.1) +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label",
       color = "Capitalized Label") +
  scale_x_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  scale_color_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  theme_classic()
```

***Description: Depends on their plot***

6.  Create a scatter plot. Change the color of the points to create a multiple scatter plot. Write 1-2 sentences describing what information you can gather from plot. (4 points)

```{r warning=FALSE}
# Scatterplot
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color = island)) +
  geom_point() +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label",
       color = "Capitalized Label") +
  scale_color_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  theme_light()
```

***Description: Depends on their plot***
