---
title: "Module 2, Assignment 2"
author: "Ellen Bledsoe"
date: "2023-02-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

## Data Summary

1.  As always, we start by loading the `tidyverse`. (1 point)

    ```{r message = FALSE}
    # Load library
    library(tidyverse)
    ```

2.  Next, we need to load in our tilapia growth dataset. Call the data frame `growth`. Then use both the `head` and `tail` functions to take a look at the data. (1 point)

    ```{r}
    # Load data
    growth <- read_csv("../data/tilapia_growth.csv")

    # Head
    head(growth)

    # Tail
    tail(growth)
    ```

3.  Before we can plan any strategy, we need to understand the data that we have. Answer the following questions about the data. (0.5 points each, 2 points total)

    a\. What does one row represent? (One tank? One temperature? One treatment? One fish?) ***One fish***

    b\. How many tanks of fish were sampled? ***16***

    c\. How many fish were sampled? ***320***

    d\. How many different "percent soy protein" levels (treatments) are there? In this assignment, we will treat `perc_soy_protein` as a *categorical* variable, so another way to ask this question is: how many categories of percent soy protein do we have? ***4***

## Prediction

4.  Spend some time thinking about each one of these steps. What steps will you need to take to produce the end result? What data frame will you use? What columns will you use? What functions will you use? How will you plot things?

    For each of the 4 tasks listed above, *describe* (do NOT code) how you will get from the starting point (a data frame) to the result (another data frame or a plot).

    This question will be grade ***only on completion***, not on whether or not your plan is *correct*. (2 points)

    ***Task (a):***

    ***Task (b):***

    ***Task (c):***

    ***Task (d):***

## Execution

```{r}
# Do as.factor on perc_soy_protein
growth <- growth %>% 
  mutate(perc_soy_protein = as.factor(perc_soy_protein))
```

5.  Use the `mutate()` function to add a `day_30_weight_kg` column to the growth data frame. (2 points)

    ```{r}
    growth <- growth %>% 
      mutate(day_30_weight_kg = day_30_weight / 1000)
    ```

### Task (a)

**A data frame with the average growth (`day_30_weight_kg`) per treatment (`perc_soy_protein`)**

6.  Create a new data frame called `growth_by_treatment`. We first want to group the data by treatment (`perc_soy_protein`) then calculate the average weight in kg. (2 points)

    ```{r}
    # Add a day_30_weight_kg column to data frame
    growth <- growth %>%
      mutate(day_30_weight_kg = day_30_weight / 1000)

    # View
    print.data.frame(head(growth))
    ```

### Task (b)

**A box plot that shows the relationship (or lack thereof) between percent soy protein in the diet and the weight at 30 days**

7.  Make a box plot with `perc_soy_protein` on the x-axis (horizontal) and `day_30_weight_kg` on the y-axis (vertical). Change the axis labels to be more easily understood and add a theme. (2 point)

    ```{r}
    # Box plot percent soy protein in the diet v. the weight at 30 days
    ggplot(growth, aes(perc_soy_protein, day_30_weight_kg)) +
      geom_boxplot() +
      geom_jitter(width = 0.1) +
      labs(x = "Percent Diet Comprised of Soy Protein",
       y = "Tilapia Weight at 30 Days (kg)") +
      theme_light()
    ```

### Task (c)

**A data frame with the average growth per treatment (`perc_soy_protein`) *and* if tanks are warm or cold**

8.  Now that we have our `tank_category` column, we can use it in our `group_by` function, along with `perc_soy_protein`, to calculate the average `day_30_weight_kg` for warm and cold tanks in each treatment. Call this new data frame `growth_by_temp_treatment`. (2 points)

    ```{r}
    # Average growth per treatment (perc_soy_protein) and if tanks are warm or cold
    growth_by_treatment_and_temp <- growth %>%
      group_by(perc_soy_protein, tank_category) %>%
      summarise(mean_weight_kg = mean(day_30_weight_kg))

    # View
    growth_by_treatment_and_temp
    ```

### Task (d)

**A scatter plot that show the relationship (or lack thereof) between average tank temperature and the weight at 30 days**

9.  Make a multiple scatter plot with `avg_tank_temp` (not `tank_category`!) on the x-axis (horizontal) and `day_30_weight_kg` on the y-axis (vertical). Change the color so it represents the percent soy protein. Change the axis labels to be more easily understood and add a theme. (2 point)

    ```{r}
    # Scatterplot average tank temperature v. the weight at 30 days
    ggplot(growth, aes(avg_tank_temp, day_30_weight_kg, color = perc_soy_protein)) +
      geom_point() +
      labs(x = "Average Tank Temperature (C)",
       y = "Tilapia Weight at 30 Days (kg)",
       color = "Percent Soy Protein") +
      theme_light()
    ```

## Reflection

10. Imagine we had decided to treat `perc_soy_protein` as a continuous variable. What type of plot we have used for task (b)? Would we have been able to complete task (d)? Why or why not? (2 points)

    ```{r}
    # Answer: Yes or no is acceptable. 

    # I have not taught them how to plot 3 continuous variables on a scatter plot, but it is doable. If they say no, you can only plot 2 continuous and 1 categorical, that is valid. If they say you can plot 3 because you can use color as a spectrum, that is also viable. Just make sure they explain why it would (or would not) work.
    ```

11. Write 3-5 sentences about if and how your predictions and execution differed and what you learned through the process. (3 points)

    *Examples of questions to answer: How did your initial prediction of how you expected to accomplish the 4 tasks match up with how we actually went about doing it? Were they similar? Were there common mistakes that you made beforehand? Did you plan a different execution from what we did above that you think would also work?*

    ***Answer:***
