---
title: "Module 1 Assignment 3: Getting to Know your Home"
author: "Ellen Bledsoe"     # <- your name here!
date: "`r Sys.Date()`"      # <- uses the current date when rendered
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

1.  In your own words, describe what the `tidyverse` is. Your answer should be between 1-3 sentences.

    ***Should mention:***

2.  Load in the `tidyverse` package.

```{r load_tidyverse}
# Load packages
library(tidyverse)
```

3.  Load in the data file (called aggregated_station_data.csv) using the `read_csv()` function. Save the data as an object called `weather`.

```{r load_data}
# Read in weather station data
weather <- read_csv("../data/aggregated_station_data.csv")
```

4.  Take a look at the data in whichever way you would like (e.g., `glimpse()`, `slice()`, `str()`, `head()`, etc.). How many rows and columns are in the data? Type your answers below:

    ***Rows: 139, 160***

    ***Columns: 12***

5.  Create a new data frame that only includes temperatures which are above freezing (AKA greater than 0).

```{r paged.print=TRUE}
# Only temperatures above freezing
filter(weather, temp > 0)
```

6.  Create a new data frame that includes *only* the following columns: year, day, month, temp, station_id. Save this new data frame as an object called `station_temp`.

```{r temp_df}
# Filter columns to year, day, month, temp, and station_id
station_temp <- select(weather, year:month, temp, station_id)

# View
station_temp
```

7.  Using the data frame you created in Q6 above (`temp`), add a new column to that data frame that converts the temperature column (currently in Celsius) to Fahrenheit. Call the new column `tempF`.

```{r tempF}
# Add new column that converts the temperature column (in C) to F
station_temp %>% 
  mutate(tempF = temp*(9/5) + 32)
```

8.  In *your own words* (either bullet points or sentence form is fine), explain two benefits of using the pipe (`%>%`).

    ***Should mention:***

9.  Using the *original* data frame (`weather`), find the minimum temperature recorded for each month (in Celsius, the original column called `temp`). (Hint: think about months first (split) and then temperature (apply). You will also want to remove all the NA values.)

```{r min_temp}
# Minimum temperature for each month
weather %>% 
  group_by(month) %>% 
  summarise(min_temp = min(temp, na.rm = TRUE))
```

10. Again, using the *original* data frame, create a data frame with the mean temperature for the month of January for each station.

```{r mean_jan_temp}
# Data frame with the mean January temperature for each station
weather %>% 
  filter(month == 1) %>% 
  group_by(station_id) %>% 
  summarize(mean_temp = mean(temp, na.rm = TRUE))
```

## Bonus! (up to 2 points)

Write code to determine how many unique stations are in the `weather` data set. (Hint: look up the help file for the `distinct()` and the `count()` functions).

```{r unique_stations}
# Number of unique stations
weather %>% 
  distinct(station_id) %>% 
  count() 
```
