---
title: "Module 1, Assignment 2: Getting to Know the Team"
author: "Ellen Bledsoe"     # <- your name here!
date: "`r Sys.Date()`"      # <- uses the current date when rendered
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

## Vectors

```{r vector}
# Vector with counts of penguins
counts <- c(2, 9, 4, 3, 6, 7, 1, 0, 3)
```

1.  What data class is `counts`? Write a line of code that tells you.

```{r data_class}
# Data class for counts
class(counts)
```

2.  Write a line of code that pulls out the 2nd value in the `counts` vector.

```{r second_value}
# Second value of counts vector
counts[2]
```

3.  Calculate the average number of penguins that were counted.

```{r avg_penguins}
# Mean number of penguins
mean(counts)
```

## Data Frames

```{r import_data}
# Import data
team_data <- read.csv("../data/team_antarctica_responses.csv")
```

4.  Take a look at the data frame using the `head()` function.

```{r examine_data}
# First 10 rows of data
head(team_data, 10)
```

5.  Using what you know about sub-setting data frames, write a line of code the pulls out the parka color for UniqueID 9 (row 9).

```{r parka7}
# Parka color for UniqueID 9
team_data[9, 7]
```

6.  On average, how did people rate their ability to be in a remote location?

```{r average_cold_tolerance}
# Average rating to live in a remote location
mean(team_data$remote_location)
```

7.  What are the minimum and maximum distances that would be traveled by a team member to get to Antarctica? Use the `min()` and `max()` functions.

```{r min_max_distance}
# Minimum distance
min(team_data$distance_mi)

# Maximum distance
max(team_data$distance_mi)
```

8.  Create a data frame that only includes rows of data for people who rated their fishing skills as a 5.

```{r cooking_skill}
# Dataframe with only those with fishing skill rating of 5
team_data[team_data$fishing_skill == 1, ]
```

9.  Write a line of code that tells us what data class the `good_with_animals` column is.

    ```{r}
    # Data class of a column
    class(team_data$good_with_animals)
    ```

10. Calculate the average cold tolerance of people who want blue parkas.

```{r parka_colors}
# Average cold tolerance of people with blue parkas
mean(team_data[team_data$parka_color == "Blue", 4])
```

## Bonus (up to 2 points)!

What animal should be on our team flag?

```{r flag_mascot}
# data frame
mascot <- team_data$flag_mascot

# mascot count
table(mascot)
```

***Answer: Penguin***
