---
title: "Module 4 Assignment 1"
author: "Ellen Bledsoe"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

### Set-Up

```{r message = FALSE}
# Load library
library("tidyverse")

# Load data
hairgrass <- read_csv("../data/hairgrass_data.csv")
```

### Phosphorus Content

1.  Calculate the mean and standard deviation of the measured phosphorus content.

```{r}
# Mean and standard deviation - phosphorus
hairgrass %>% 
  summarize(mean_P = mean(p_content), 
            stdev_P = sd(p_content))
```

2.  Which variable is the independent variable? Which is the dependent?

    ***Independent: phosphorus***

    ***Dependent: hairgrass***

3.  Create a scatter plot of hair grass density and phosphorus content (don't add the line of best fit yet). Be sure to make the labels easier to understand and add a theme.

```{r}
# Scatterplot
ggplot(hairgrass, aes(x = p_content, y = hairgrass_density_m2)) +
  geom_point() +
  labs(x = "Phosphorus Content",
       y = "Hair Grass Density (m^2)") +
  theme_classic()
```

4.  Write 1-2 sentences interpreting the plot above. Is this a positive relationship, negative relationship or no relationship at all? Based on your prediction, do you think the correlation coefficient will be positive, negative, or zero?

    ***Answer: Looks like no relationship, therefore the correlation coefficient will be close to 0***

5.  Calculate the correlation coefficient, `r`.

```{r}
# Correlation coefficient
r <- cor(y = hairgrass$hairgrass_density_m2, x = hairgrass$p_content)

# View
r
```

6.  Calculate the `r^2` value. Write a one sentence interpretation of what the `r^2` value means in the context of these two variables.

```{r}
# R-squared
r^2 
```

***Interpretation:*** **This means that less than 1% of the variation in hair grass density can be explained by variation in phosphorus content.**

7.  What are the null and alternative hypothesis regarding the relationship between these two variables? (2 pts)

    ***Null: There is no relationship between hairgrass density and phosphorus content***

    ***Alternative: There is a relationship between hairgrass density and phosphorus content***

8.  Create the scatter plot that includes the line of best fit (have `ggplot2` calculate the linear equation for you). Again, make the labels clearer and add a theme

```{r}
# Scatterplot
ggplot(hairgrass, aes(x = p_content, y = hairgrass_density_m2)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Phosphorus Content per 100mL",
       y = "Hairgrass Density per m^2") +
  theme_classic()
```

9.  Using code, create the regression model in R and obtain the summary of it.

```{r}
# Linear model
mod <- lm(hairgrass_density_m2 ~ p_content, data = hairgrass)

# Results
summary(mod) # 1pt
```

10. Write out the equation for the line of best fit using the values and variables from the results above.

    ***Answer: hairgrass density = -0.010\*phosphorus + 7.97***

11. Interpret the model summary. What is the p-value for our variable of interest? Do we accept or reject the null hypothesis regarding the relationship between these two variables? What can we conclude then about building a road? (2 pts)

    ***Answer: the p-value is 0.5538, so we do not reject the null hypothesis. There is not a relationship between phosphorus content and hairgrass density, so we don't need to take it into account for our road***

    ***Note: If they put in the wrong variables and get the incorrect model, they can still get the rest of the points as long as they interpret the one they made correctly.***

### Summer Temperature

Now let's do the same thing for the average summer temperatures.

12. Create a scatter plot of hair grass density and average summer temperature. Remember to improve the axes labels and add a theme!

```{r}
# Scatterplot
ggplot(hairgrass, aes(x = avg_summer_temp, y = hairgrass_density_m2)) +
  geom_point() +
  labs(x = "Average Summer Temperature (C)",
       y = "Hairgrass Density (m^2)") + 
  theme_bw()
```

13. Write 1-2 sentences interpreting the plot above. Is this a positive relationship, negative relationship or no relationship at all? Based on your prediction, do you think the correlation coefficient will be positive, negative, or zero?

    ***Answer: Positive relationship; r will be positive***

14. Calculate the correlation coefficient, `r`.

```{r}
# Correlation coefficient
r <- cor(y = hairgrass$hairgrass_density_m2, x = hairgrass$avg_summer_temp)

# View
r
```

15. Calculate the `r^2` value. Write a one sentence interpretation of what the `r^2` value means in the context of these two variables.

```{r}
# R-squared
r^2 
```

***Interpretation: This means that 40% of the variation in hair grass density can be explained by variation in average summer temperature.***

16. Create the scatter plot that includes the line of best fit (have `ggplot2` calculate the linear equation for you). Make the labels easier to interpret and add a theme.

```{r}
# Scatterplot
ggplot(hairgrass, aes(x = avg_summer_temp, y = hairgrass_density_m2)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Hairgrass Density (m^2)") +
  xlab("Average Summer Temperature (C)") +
  theme_bw()
```

17. Using code, create the regression model in R and obtain the summary of it.

```{r}
# Linear model
mod <- lm(hairgrass$hairgrass_density_m2 ~ hairgrass$avg_summer_temp)

# View
summary(mod) 
```

18. Interpret the model summary. What is the p-value for our variable of interest? Do we accept or reject the null hypothesis regarding the relationship between these two variables? What can we conclude then about building a road? (2 points)

    ***Answer: p-value is \<2e-16, so super small and highly significant; reject the null; should think about temperature when we decide where to build the road***
