---
title: "Practice for the Final"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

## Set-Up

```{r message = FALSE}
# Load libraries
library(tidyverse)
library(palmerpenguins)
```

```{r}
# Show in Environment
penguins <- penguins
```

## Problem Set 1

```{r}
# Filter Dream island
dream <- penguins %>% 
  filter(island == "Dream")
```

Based on our question, which variable is independent and which is dependent? Which is continuous and/or which is categorical?

-   ***flipper length: dependent, continuous***

-   ***species: independent, categorical***

First, calculate the range (minimum and maximum) and mean of the flipper lengths for each species

```{r}
# Minimum, maximum, and mean - flipper lengths
dream %>% 
  group_by(species) %>% 
  summarise(min_flipper = min(flipper_length_mm, na.rm = TRUE),
            max_flipper = max(flipper_length_mm, na.rm = TRUE),
            mean_flipper = mean(flipper_length_mm, na.rm = TRUE))
```

Choose an effective visualization method for this data. Use `ggplot2`.

```{r}
# Boxplot, multiple histogram, or multiple density plot are all acceptable

# Boxplot
ggplot(dream, aes(x = species, y = flipper_length_mm, color = species)) +
  geom_boxplot() +
  geom_jitter(width = 0.1, alpha = 0.5) +
  labs(x = "Species",
       y = "Flipper Length (mm)",
       color = "Species") +
  theme_classic()
```

Write out the null and alternative hypotheses.

-   ***Null:***

-   ***Alternative:***

Run the appropriate statistical test.

```{r}
# t-test
t.test(data = dream, flipper_length_mm ~ species)
```

Interpret the results of your statistical test:

-   What is the p-value?
-   Is the p-value above or below 0.05?
-   What does your answer to the question above mean?
-   Should we reject or fail to reject the null hypothesis?

***Answers:***

Should we run pairwise comparisons? If yes, do so below and interpret:

***No need, only 1 pair compared***

## Problem Set 2

First, calculate the mean and standard deviation for both bill length and flipper length.

```{r}
# Mean and standard deviation - bill and flipper length
bill_flipper <- penguins %>% 
  summarise(mean_bill = mean(bill_length_mm, na.rm = TRUE),
            sd_bill = sd(bill_length_mm, na.rm = TRUE),
            mean_flipper = mean(flipper_length_mm, na.rm = TRUE),
            sd_flipper = sd(flipper_length_mm, na.rm = TRUE))

# View
bill_flipper
```

Choose the best way to visualize the relationship between these two variables

```{r}
# Scatterplot
ggplot(penguins, aes(flipper_length_mm, bill_length_mm)) +
  geom_point() +
  geom_smooth(method = "lm") +
    labs(x = "Flipper Length (mm)",
         y = "Bill Length (mm)") +
  theme_bw()
```

To do the rest of this problem set, the easiest way is to create a new data frame with no NA values. Run the code chunk below and use that new data frame for the rest of the problem set.

```{r}
# Remove NA values
penguins_noNA <- penguins %>% 
  filter(!is.na(bill_length_mm),
         !is.na(flipper_length_mm))
```

Calculate the correlation coefficient and the `r^2` value.

```{r}
# Correlation coefficient
r <- cor(x = penguins_noNA$flipper_length_mm, y = penguins_noNA$bill_length_mm)

# View
r

# R-squared * 100
r^2 * 100
```

-   According to the correlation coefficient, is the relationship positive, negative or is there no relationship?

    ***Answer:***

```{=html}
<!-- -->
```
-   What does the `r^2` value tell us? Remember, we usually multiply the `r^2` by 100 to represent this as a percentage.

    ***Answer:***

Run the appropriate statistical test for this data.

```{r}
# Linear model
lm_model <- lm(data = penguins_noNA, bill_length_mm ~ flipper_length_mm)

# Results
summary(lm_model)
```

Using variables and numbers from the summary above, write out the equation of the line of best fit.

```{r}
# Answer: bill_length_mm = (0.25 * flipper_length_mm) - 7.26
```

Interpret the results of your statistical test:

-   What is the p-value?
-   Is the p-value above or below 0.05?
-   What does your answer to the question above mean?

***Answers:***

Should we run pairwise comparisons? If yes, do so below and interpret:

***No pairs to compare***

### Adding a Variable

First, plot the data, this time including species as a variable in the plot.

```{r}
# Scatterplot
ggplot(penguins, aes(flipper_length_mm, bill_length_mm, color = species)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Flipper Length (mm)",
       y = "Bill Length (mm)", 
       color = "Species") +
  theme_bw()
```

Run the model again, this time including species and the species *interaction* with "independent" variable.

```{r}
# Linear model with interaction
mlm_model <- lm(data = penguins_noNA, bill_length_mm ~ flipper_length_mm * species)

# Results
summary(mlm_model)
```

Interpret the results from the model above. Focus on the p-values for the independent variables and/or interaction terms, not the overall model.

***Answer:***

## Problem Set 3

First, calculate the minimum, maximum, and mean of the body mass for each species. Call this dataframe `body_mass`.

```{r}
# Minimum, maximum, and mean
body_mass <- penguins %>% 
  group_by(species) %>% 
  summarise(min_mass = min(body_mass_g, na.rm = TRUE),
            max_mass = max(body_mass_g, na.rm = TRUE),
            mean_mass = mean(body_mass_g, na.rm = TRUE))

# Results
body_mass
```

What if we wanted the values in the newly created `body_mass` column to be in kilograms instead of grams?

Our first step is to write a function that converts a number (not a column, mind you) from grams to kilograms.

```{r}
# Conversion function
g_to_kg <- function(g){
  kg <- g / 1000
  print(kg)
}
```

Convert all the columns in the `body_mass` data frame from grams to kilograms using the function you wrote above. You don't need to save this dataframe as anything, but if you do, call it `body_mass_kg`.

```{r}
# Convert values in dataframe
body_mass %>% 
  mutate(min_mass = g_to_kg(min_mass),
         max_mass = g_to_kg(max_mass),
         mean_mass = g_to_kg(mean_mass))

# Alternative option:

# Copy code from above
# Then add a mutate function before the summarise function,
# and modify summarise function columns

penguins %>% 
  group_by(species) %>% 
  mutate(body_mass_kg = g_to_kg(body_mass_g)) %>% 
  summarise(min_mass = min(body_mass_kg, na.rm = TRUE), # body_mass_kg instead of body_mass_g
            max_mass = max(body_mass_kg, na.rm = TRUE),
            mean_mass = mean(body_mass_kg, na.rm = TRUE))
```

Back to the question at hand... choose an effective visualization method for this data (you will want to use the original `penguins` dataframe --- and grams are fine). Practice adding lines that represent to mean values in the plot. Thinking critically about which columns to use!

```{r}
# Density plot, with mean line
ggplot(penguins, aes(x = body_mass_g, fill = species)) +
  geom_density(alpha = 0.5) +
  geom_vline(data = body_mass, aes(xintercept = mean_mass, color = species)) +
  labs(x = "Body Mass (g)",
       y = "Density/Frequency",
       fill = "Species",
       color = "Species") +
  theme_classic()
```

Write out the null and alternative hypotheses.

-   ***Null:***

-   ***Alternative:***

Run the appropriate statistical test.

```{r}
# ANOVA
aov_mod <- aov(data = penguins, body_mass_g ~ species)

# Results
summary(aov_mod)
```

Interpret the results of your statistical test:

-   What is the p-value?
-   Is the p-value above or below 0.05?
-   What does your answer to the question above mean?
-   Should we reject or fail to reject the null hypothesis?

***Answers:***

Should we run pairwise comparisons? If yes, do so below and interpret:

```{r}
# Pairwise comparisons
TukeyHSD(aov_mod)
```

***Interpretation:***
