---
title: "Module 4 Assignment 2"
author: "Ellen Bledsoe"
date: "2022-12-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

## Set-Up

1.  As always, let's load the `tidyverse` to get started.

```{r, message = FALSE}
# Load library
library(tidyverse)
```

2.  Now read in the data set, which is called `nonvascular_plants.csv`. Name the data frame `plants`.

```{r}
# Load data
plants <- read_csv("../data/nonvascular_plants.csv")
```

3.  Take a look at the data; use the `head()` and `tail()` functions to look at the beginning of the data set and the end of the data set respectively. (2 points)

```{r}
# Head
head(plants)

# Tail
tail(plants)
```

## Regression

4.  Which of our two variables is dependent and which is independent (hint: re-read the introduction if you're feeling confused). Determine whether each is continuous or categorical. (2 points)

-   ***`penguin_density_m2`: independent, continuous***
-   ***`percent_plant_cover`: dependent, continuous***

5.  Plot the data (disregard plant type for now) using the appropriate plot from `ggplot2`. Remember to add a line of best fit (and remember to make that line a straight line using the `method = "lm"` argument!). Modify the axes labels and add a theme. (2 points)

```{r}
# Scatterplot
ggplot(plants, aes(penguin_density_m2, percent_plant_cover)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Penguin Density (per m^2)",
       y = "Percent Plant Cover") +
  theme_bw()
```

6.  Calculate the correlation coefficient. What does this tell us about the relationship? (2 points)

```{r}
# Correlation coefficient
r <- cor(plants$penguin_density_m2, plants$percent_plant_cover)

# View
r
```

***Answer: perhaps a slight negative relationship but probably none at all***

7.  Calculate R\^2. How much variation does our line of best fit explain (report in %)? (2 points)

```{r}
# R-squared
r^2 * 100
```

***Answer: 0.3% aka not very much***

8.  Run a linear regression model for these days and interpret the results. Does it seem like penguin density is a significant driver of plant cover? (3 points)

```{r}
summary(lm(data = plants, percent_plant_cover ~ penguin_density_m2))
```

***Answer: p \> 0.05 so not a likely driver of plant cover***

## Multiple Regression and Interaction

9.  First, let's plot the data again, but this time make the color different for each type of plant. Again, adjust all necessary labels and add a theme. (2 points)

```{r}
# Scatterplot
ggplot(plants, aes(penguin_density_m2, percent_plant_cover, color = plant_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Penguin Density per m^2",
       y = "Percent Plant Cover") +
  theme_minimal()
```

10. Run a multiple regression model, incorporating the plant type into the model using the `*` notation. Write 2-3 sentences interpreting the results. (3 points)

    ```{r}
    summary(lm(data = plants, percent_plant_cover ~ penguin_density_m2 * plant_type))
    ```

-   Which variables are significant? How do we know?

-   Is the interaction term significant? How do we know?

    ***Answer: all variables are highly significant including the interaction term--all p \< 0.05***
