---
title: "Module 3: Assignment 2"
author: "Ellen Bledsoe"
date: "2022-11-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

## Set-Up

1.  As always, our first order of business is to load the `tidyverse` and our datasets. For this assignment, we have two different datasets: one for our survey of fish amounts and one for seal observations. Read both of them into the workspace and name them `fish` and `seals`, respectively.

```{r message = FALSE}
# Load library
library(tidyverse)

# Load data
fish <- read_csv("fish.csv")
seals <- read_csv("seals.csv")
```

## Fish

```{r}
head(fish)
```

### Conceptual

2.  Write out our two hypotheses for these data.

    **Null Hypothesis** $H_{0}$: ***No difference in amount of fish per bay***

    **Alternative Hypothesis** $H_{0}$: ***Difference in amount of fish per bay***

### Numeric

3.  Let's first find out what the mean (average) and standard deviation (spread) of `fish_kg` is in each bay. Save this data in a new data frame called `fish_summary`.

```{r}
# Mean and standard deviation of fish weight
fish_summary <- fish %>% 
  group_by(bay) %>% 
  summarise(mean_fish = mean(fish_kg),
            sd_fish = sd(fish_kg))

# View
fish_summary
```

### Visual

4.  Plot the fish data using a box-and-whisker plot. It doesn't need to be fancy (no need to fix axis labels and such) but be sure it has the following:

    -   Data points overlaying the boxes
    -   The points should be partially transparent and jittered

```{r}
# Box and whisker
ggplot(fish, aes(bay, fish_kg)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.5, width = 0.1) 
```

### Statistics

5.  In our data set, which variable is the independent variable? Is it categorical or continuous? Which is the dependent variable and is it categorical or continuous?

    **Independent:** ***bay - categorical***

    **Dependent:** ***fish_kg - continuous***

6.  Run an ANOVA to determine if there is an overall difference in means in the four bays. Save the model as an object called `fish_model`, then display the results of the model using the `summary()` function. Remember, the syntax for the model is: `dependent ~ independent`

```{r}
# ANOVA
fish_model <- aov(data = fish, fish_kg ~ bay)

# Results
summary(fish_model)
```

7.  Interpret the results of the model and answer the following questions (2 points):

    -   What is the value of the test statistic? ***1.751***
    -   What is our p-value? ***0.155***
    -   Is our p-value higher or lower than our cut-off value of 0.05? ***Higher***
    -   Write 2-3 sentences explaining that this result means. How do we interpret this value? What does it mean for our hypotheses?

    ***Answers: No significant difference in the amount of fish per bay, fail to reject null***

8.  Run some code to compute pairwise comparisons.

```{r}
# Pairwise comparisons
TukeyHSD(fish_model)
```

9.  Write 2-3 sentences interpreting the pairwise comparisons. Which pairs of bays are significantly different from each other, if any?

    ***Answer: None are different from each other (all above 0.05)***

## Seals

### Conceptual

10. Write out our 2 hypotheses for the seal data.

    ***Null: No difference in seals by bay***

    ***Alternative: Difference in \# of seals by bay***

### Numeric

11. Calculate the mean and standard deviation for the number of seals in each bay. Save this to a new data frame called `seal_summary`.

```{r}
# Mean and standard deviation of number of seals
seal_summary <- seals %>% 
  group_by(bay) %>% 
  summarise(mean_fish = mean(num_seals),
            sd_fish = sd(num_seals))

# View
seal_summary
```

### Visual

12. Plot the seal using a box-and-whisker plot. It doesn't need to be fancy (no need to fix axis labels and such) but be sure it has the following:
    -   Data points overlaying the boxes
    -   The points should be partially transparent and jittered

```{r}
# Box and whisker plot
ggplot(seals, aes(bay, num_seals)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.5, width = 0.1) 
```

### Statistics

13. Run the appropriate statistical model to determine if there is an overall difference in means in the four bays. Save the model as an object called `seal_model`, then display the results of the model using the `summary()` function.

```{r}
# ANOVA
seal_model <- aov(data = seals, num_seals ~ bay)

# Results
summary(seal_model)
```

14. Interpret the results of the model and answer the following questions (2 points):

    -   What is the value of the test statistic? ***1467***
    -   What is our p-value? ***\<2e-16***
    -   Is our p-value higher or lower than our cut-off value of 0.05? ***Lower***
    -   Write 2-3 sentences explaining that this result means. How do we interpret this value? What does it mean for our hypotheses?

    ***Answers: Differences in num of seal per bay, reject null***

15. Run some code to compute pairwise comparisons.

```{r}
# Pairwise comparisons
TukeyHSD(seal_model)
```

16. Write 2-3 sentences interpreting the pairwise comparisons. Which pairs of bays are significantly different from each other, if any?

    ***Answer: All pairs are sig. difference except Sulzberger and Hope***

## Decision-Making

17. Based on *all* our results, which two bays do you think we should fish? Explain your rationale (2 points)

    ***Answer: Because there is no difference in the number of fish per bay, we will want to make our decision based on seal numbers. We are looking for the lowest seal numbers, which Sulzberger and Hope have. The other bays have significantly higher seal numbers than either of these two, so we would choose them.***
