---
title: "Module 2, Assignment 3"
author: "Ellen Bledsoe"     # <- your name here!
date: "`r Sys.Date()`"      # <- uses the current date when rendered
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{{r message=FALSE}}
library(palmerpenguins)
library(tidyverse)
```

# Student Answer Key

### This document contains the answers to the assignment without the code that produces it.

### REMINDER: Because I'm having you choose your own variables, the examples in the provided Answer Key likely will not match yours (though they might). You should strive to produce a plot that looks *similar in style* to those in the Answer Key, but the number of categories and the actual data points will likely be different.

1.  

```{r}
# Load libraries
library(tidyverse)
library(palmerpenguins)
```

2.  

```{r}
# Answer:

# species:

# island:

# bill_length_mm:

# bill_depth_mm:

# flipper_length:

# body_mass_g:

# sex:

# year: continuous
```

3.  

```{r warning=FALSE, message=FALSE, fig.width=5, fig.height=4}
# Histogram
ggplot(penguins, aes(bill_depth_mm)) +
  geom_histogram(bins = 20) +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label") +
  theme_bw()
```

```{r}
# Description:
```

4.  

```{r warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
# Multiple density plot
ggplot(penguins, aes(body_mass_g, color = island, fill = island)) +
  geom_density(alpha = 0.5) +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label",
       color = "Capitalized Label",
       fill = "Capitalized Label") +
  scale_fill_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  scale_color_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  theme_bw()
```

```{r}
# Description:
```

5.  

```{r warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
# Box-and-whisker plot
ggplot(penguins, aes(species, flipper_length_mm)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.5, width = 0.1) +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label") +
  scale_x_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  theme_classic()
```

```{r}
# Description:
```

6.  

```{r warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
# Scatterplot
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color = island)) +
  geom_point() +
  labs(x = "Descriptive Axis Label",
       y = "Descriptive Axis Label",
       color = "Capitalized Label") +
  scale_color_discrete(labels = c("[redacted]", "[redacted]", "[redacted]")) +
  theme_light()
```

```{r}
# Description:
```
