---
title: "Module 2, Assignment 1"
author: "Ellen Bledsoe"
date: "2023-09-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructor Key

### This document contains the answers to the assignment WITH the code that produces it.

1.  Load the `tidyverse` package into the work space.

    ```{r, message = FALSE}
    # Load library
    library(tidyverse)
    ```

2.  Read in the data using the `read_csv()` function. Name the data frame `sick_fish`.

    ```{r}
    # Load data
    sick_fish <- read_csv("../data/fish_sick_data.csv")
    ```

3.  Use the `head()` function to take a look at the columns in the data frame.

    ```{r}
    # Look at columns and first few rows in dataframe
    head(sick_fish)
    ```

4.  How many rows does the data frame have? How many columns?

    ***Answer: 50 rows, 7 columns***

5.  Take a look at the data frame.

    -   What does one row (observation) represent (e.g., an individual fish?, all fish of a certain species? all tanks of a certain species? etc.)? (1 point)

        ***Answer: One row represents one fish tank that was sampled***

    -   Based on the column names, briefly (just a few words) describe what data is included in each column. (2 points)

        ***Answers:***

        -   ***tank_id = identifier for individual tanks***

        -   ***species = fish species in the tank***

        -   ***avg_daily_temperature = average water temp in the tank***

        -   ***num_fish = total number of fish in the tank***

        -   ***day_length = amount of daylight provided for tanks***

        -   ***tank_volume = water volume in the tank***

        -   ***num_sick = number of sick fish per tank***

6.  Take a look at the columns that have the total number of fish in the tank and the number of sick fish per tank. Determine whether these two columns are continuous or categorical.

    ***Answer: Both num_fish and num_sick are continuous***

7.  Using base R, create a scatter plot. Put the total number of fish on the x-axis and the number of sick fish on the y-axis.

    ```{r}
    # Scatterplot
    plot(sick_fish$num_fish, sick_fish$num_sick)
    ```

8.  Interpret the scatter plot. What is the plot telling you? Is there a positive or negative relationship between the two variables. What does that mean? (2 points)

    ***Answer: Negative relationship, meaning that the more fish that are in the tank, the fewer sick fish there are (which is counter-intuitive).***

9.  Create the scatter plot using the proper `geom` function.

    ```{r}
    # Scatterplot with geom
    ggplot(sick_fish, aes(num_fish, num_sick)) +
      geom_point()
    ```

10. Now, add to the plot that we created above to make it clearer to understand. Add better axes labels and choose a theme. (2 point)

    ```{r}
    # Plot above with labels and theme
    ggplot(sick_fish, aes(num_fish, num_sick)) +
      geom_point() + 
      labs(x = "Total Number of Fish per Tank",
           y = "Number of Sick Fish per Tank") +
      theme_bw()
    ```

11. For *each* fish species, calculate the average and the standard deviation for the number of sick fish. (2 points)

    ```{r}
    # Mean and standard deviation
    sick_fish %>% 
      group_by(species) %>% 
      summarise(mean_sick = mean(num_sick),
            sd_sick = sd(num_sick))
    ```

12. Based on the summary data you've calculated above, do you think the two clumps of data correspond to the two species? Which species seems to be the one that is causing the most problems? (2 points)

    ***Answer: Seems like trout are driving the issues; seems reasonable that clumps could belong to species***

13. Do some brainstorming. Based on the plots we've made and the calculations we've done so far, are we *sure* that the two clumps of data we see in the data visualization do, in fact, correlate to the two different species? How could we confirm? How might we include that information in the plot? (2 points)

***Answer: Many answer options here.***

-   ***Could take average of total num fish to see if that corresponds to what is on the plot***

-   ***Could change some characteristic of the plot (point shape, color, size) to represent fish species***

-   ***Could add labels (would get busy)***
